\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-07-07 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
Add kernel visualization png file for examples/homogenous_halfspace.

\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the}
and Section \ref{sec:Using-tomographic} `Using external tomographic
Earth models' for further details. 
\end{itemize}
\item [{nodes\_coords\_file}] Contains the point locations in Cartesian
coordinates of the mesh element corners. 
\item [{mesh\_file}] Contains the mesh element connectivity. The hexahedral
elements can have 8 or 27 nodes.\\
 See picture doc/mesh\_numbering\_convention/numbering\_convention\_27\_nodes.jpg
to see\\
 in which (standard) order the points must be cited. In the case of
8 nodes, just include the first 8 points. 
\item [{free\_or\_absorbing\_surface\_file\_zmax}] Contains the free surface
connectivity or \\
 the surface connectivity of the absorbing boundary surface at the
top (Zmax), \\
 depending on whether the top surface is defined as free or absorbing
in DATA/Par\_file. \\
 You should put both the surface of acoustic regions and of elastic
regions in that file; that is, list all the element faces that constitute
the surface of the model in that file. 
\item [{absorbing\_surface\_file\_xmax}] Contains the surface connectivity
of the absorbing boundary surface at Xmax \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_xmin}] Contains the surface connectivity
of the absorbing boundary surface at Xmin \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_ymax}] Contains the surface connectivity
of the absorbing boundary surface at Ymax \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_ymin}] Contains the surface connectivity
of the absorbing boundary surface at Ymin \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_bottom}] Contains the surface connectivity
of the absorbing boundary surface at the bottom (Zmin) \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\end{description}
These mesh files are needed as input files for the partitioner \texttt{xdecompose\_mesh}
to load-balance the mesh. Please see the next section for further
details.

>>>>

\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the}
and Section \ref{sec:Using-tomographic} `Using external tomographic
Earth models' for further details. 
\end{itemize}
\item [{nodes\_coords\_file}] Contains the point locations in Cartesian
coordinates of the mesh element corners. 
\item [{mesh\_file}] Contains the mesh element connectivity. The hexahedral
elements can have 8 or 27 nodes.\\
 See picture doc/mesh\_numbering\_convention/numbering\_convention\_27\_nodes.jpg
to see\\
 in which (standard) order the points must be cited. In the case of
8 nodes, just include the first 8 points. 
\item [{free\_or\_absorbing\_surface\_file\_zmax}] Contains the free surface
connectivity or \\
 the surface connectivity of the absorbing boundary surface at the
top (Zmax), \\
 depending on whether the top surface is defined as free or absorbing
(\texttt{STACEY\_INSTEAD\_OF\_FREE\_SURFACE} in \texttt{DATA/Par\_file}). \\
 You should put both the surface of acoustic regions and of elastic
regions in that file; that is, list all the element faces that constitute
the surface of the model in that file. 
\item [{absorbing\_surface\_file\_xmax}] Contains the surface connectivity
of the absorbing boundary surface at Xmax \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_xmin}] Contains the surface connectivity
of the absorbing boundary surface at Xmin \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_ymax}] Contains the surface connectivity
of the absorbing boundary surface at Ymax \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_ymin}] Contains the surface connectivity
of the absorbing boundary surface at Ymin \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\item [{absorbing\_surface\_file\_bottom}] Contains the surface connectivity
of the absorbing boundary surface at the bottom (Zmin) \\
(also needed in the case of C-PML absorbing conditions, in order for
the code to be able to impose Dirichlet conditions on their outer
edge). 
\end{description}
These mesh files are needed as input files for the partitioner \texttt{xdecompose\_mesh}
to load-balance the mesh. Please see the next section for further
details.
